% !TEX root = ../thesis-example.tex
%
\chapter{Introduction}
\label{sec:intro}

SoftProj is a system, using which the students can make submission of their software development artifacts (e.g., models, requirements and design documents, test cases, code) as a team for review. A team needs to register first for submitting their artifacts and they have access only to their own submitted artifacts. Their every submission is grouped so that they can access to them anytime they want. A review is made in several steps. At first, when a team submits their artifacts for the first time, it is assigned to a Review Project Manager (RPM) by the Lecturer. The Lecturer has access to all the artifacts. On the other hand, the RPM has access to the artifacts of the groups that have been assigned to him/her. After that, RPM distributes the individual artifacts to at least two Reviewers. A template is provided to Reviewer by the system to review and rate the artifact. An individual deadline can be given for reviewing the individual artifacts. After submission of the reviews from Reviewers, the RPM rates them. And finally, the Lecturer rates the artifacts. The Lecturer is also able to rate the RPMs and Reviewers. A reviewer has access only to the artifact that is assigned to him/her. The Admin is responsible for making all notifications and review templates, and he/she has access to all the artifacts. After completion of all these steps, the submitter will be notified by the system to view the result. 